\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2019-11-25 sections/discussion.tex
Update discussion for final draft

% General statements
Co-occurrence associations in microbial communities will identify important interactions that drive microbial community structure and organization.
There is still much disagreement between the networks generated using various methods.
This study makes a significant effort to identify those tools and parameters that enable more accurate inference of these co-occurrence networks.
The mindpipe pipeline also enables the user to explore the effect of various tools and their combinations on their dataset of interest, thereby enabling one to identify those tools that perform their best on that particular dataset.

The different denoising/clustering methods differ mostly in their identification of sequences that are in low abundances.
Hence, they do not have much of an impact on the inferred co-occurrence networks when the sequences of abundance are removed.
However, comparison of inferred and expected reference sequences and their abundances in mock community datasets has allowed us to identify \ac{dada2} as the method which best recapitulates expected the sequence composition.
There are newer recently published methods like dbOTU3~\cite{Olesen2017} as well as older popular methods like mothur~\cite{Schloss2009} that haven't been included in the study, and are possible avenues for future investigation.

@@

\hl{Other factors that play an important role in network inference} \\
Differences in environments of the samples could lead to the inference of spurious interactions.

@@

>>>>

% General statements
Co-occurrence associations in microbial communities help identify important interactions that drive microbial community structure and organization.
There is still much disagreement between the networks generated using various methods.
This study makes a significant effort to identify those tools and parameters that enable more accurate inference of these co-occurrence networks.
We have developed mindpipe, a pipeline for 16S data analysis and inference of co-occurrence networks.
This pipeline enables the analysis of 16S sequence data using different combinations of tools and makes comparison of these results straightforward.
It also enables the user to explore the effect of various tools and their combinations on their dataset of interest, thereby enabling one to identify those tools that perform their best on that particular dataset.
The pipeline is build to be modular and hence provides for a plug-and-play architecture wherein new tools and steps can be easily added.

The different denoising/clustering methods differ mostly in their identification of sequences that are in low abundances.
Hence, they do not have much of an impact on the inferred co-occurrence networks when the sequences of low abundance are removed.
However, comparison of inferred and expected reference sequences and their abundances in mock community datasets has allowed us to identify \ac{dada2} as the method which best recapitulates expected the sequence composition.
There are newer recently published methods like dbOTU3~\cite{Olesen2017} as well as older popular methods like mothur~\cite{Schloss2009} that haven't been included in the study, and are possible avenues for future investigation.

@@

% \hl{Other factors that play an important role in network inference} \\
% Differences in environments of the samples could lead to the inference of spurious interactions.

@@

% TODO: Uses in MIND, exploration, standardization, reproducibility
